### 2017-10-13 paper/sexSelectionSpacingAppendix-ver1.tex
Initial edits of Appendix for this version

\usepackage{mathpazo}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
% \usepackage[pdftex]{graphicx}
% \usepackage[all]{xypic}
\usepackage{xyling}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[pdftex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
% \usepackage[nolists,tablesfirst]{endfloat}

@@

% \date{May 2010\\ \bigskip PRELIMINARY}
\date{March 2015}

@@

\graphicspath{{graphs/},{figures/}}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
\doublespacing

@@

\section{Why Bundle Scan and Abortion?}

The easiest way to show why a bundled service makes sense is to model 
the provider's problem first and then show that both provider and
buyer will be better off if a bundled service is offered.
Take a provider with with cost, $c_a$, of providing an abortion,
and cost, $c_s$, of providing a scan.
These costs include expenses for equipment, labor,
and possibly a premium for getting caught and prosecuted. 
The provider can either charge separately for the two services,
in which case he will charge $p_s$ for the scan and $p_a$ for
the abortion, or he can charge $p_b$ for the bundle.

The provider's profit if he offers the two services separately, $\pi_{sep}$,
to $n$ buyers, who conceive girls with the probability $p(g)$, will be
\begin{equation}
\pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
\end{equation}
The first part is profit from the customers who want a scan
and the second part is the profit from the fraction of the
original customers who conceived a girl.
If the provider instead offered the same $n$ buyers a bundle service
the profit, $\pi_{bun}$, would be
\begin{equation}
\pi_{bun} = n p_b - n c_s - p(g) n c_a,
\end{equation}
since all customers pays $p_b$, all customers get a scan 
at cost $c_s$, and the fraction $p(g)$ who conceived a girl
would receive an abortion at cost $c_a$.
A profit maximizing provider then picks bundled pricing if 
$\pi_{bun} > \pi_{sep}$, or
\begin{equation}
 p_b > p_s + p(g) p_a.
\end{equation}

Assume that buyers are risk averse and that the only motivation
for getting a prenatal sex determination test is to abort 
female fetuses and that parents will abort the fetus if the test 
show a female fetus (I will relax the last assumptions below).
Furthermore, to ease exposition assume that buyers can only
spend money on two things: consumption $c$ and prenatal sex
determinations/abortions.
For a buyer facing separate services the expected utility
is then
\begin{equation}
U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
\end{equation}
where the first part is the utility if the fetus is a boy
and the buyers therefore only spend on the scan, which
happens with probability $1-p(g)$, and the
second part is the utility if the fetus is a female
and they therefore also has to pay for the abortion,
which happens with probability $p(g)$.
For a buyer facing a bundled service the utility is simply
\begin{equation}
U = U(c-p_b).
\end{equation}

If follows from the standard assumptions about utility functions
and the risk aversion assumption that
\begin{equation}
U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
\end{equation}
In other words risk averse buyers prefer a sure thing---where they pay 
upfront---over the gamble that they either have a boy and pay only for the
scanning or have a girl and pay for both the scan and the abortion.
In fact, risk aversion implies that they are willing to pay 
\emph{more} than the expected cost.
In other words,
\begin{equation}
U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
\end{equation}
where $\delta$ is a positive number that depends on the
degree of risk aversion (the more risk averse the larger
$\delta$ is).

The provider realizes that buyers are risk averse
and therefore offer a bundle where the price is in 
the range
\begin{equation}
p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
\end{equation}
Hence, the optimal pricing scheme for both provider
and buyer is bundled pricing, where you pay a flat fee
and get the pre-natal sex determination and an abortion
if needed.
% Where the provider ends up in the possible range of
% prices depends on the nature of the provider market.

I implicitly assumed that the provider is risk-neutral.
The same result hold, however, if the provider
is risk-averse as long as there are enough potential clients.
In that case, the law of large numbers will ensure that 
the risk-neutral and risk-averse choices are the same
for the provider---essentially there is no gamble if you see 
enough clients, $p(g)$ of them will present with a female fetus 
and $1-p(g)$ with a male fetus.
In fact, it is possible for the provider to be \emph{more}
risk averse than the buyers and still prefer the bundled 
pricing scheme.

Now imagine a situation where there there is some 
uncertainty about whether a buyer will go through with
the abortion after the prenatal sex determination.
This can be represented by the probability $\rho$ that
a buyer who had a prenatal sex determination test that
showed a female fetus will go through with the abortion.
If parents know that there is probability $1-\rho$ that they
will not go through with the abortion their utility is
\begin{equation}
U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
\end{equation}
where I have made the assumption that they
are equally happy with a boy or a girl if they
are in the $1-\rho$ portion of the population that
have a prenatal sex determination which show a female
fetus but do not go through with the abortion (obviously
this cannot be the case because if they were there
would be no point in having the prenatal sex determination,
but if I can show that the bundle price arise here it
would trivially hold if there were some lower utility
associated with having a girl than a boy).

Because the buyers are still risk averse they would continue
to prefer the ``sure'' thing over the gamble
\begin{equation}
U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
\end{equation}
The provider still offers a bundle, but the price is now 
in  the range
\begin{equation}
p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
\end{equation}
where $\delta$ still depends on the degree of risk aversion.

If parents on the other hand initially believe that they will always
go through with the abortion if the fetus is female but
still have probability $1-\rho$ that they will not, they would
be back to the original comparison of the utility.
\begin{equation}
U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
\end{equation}
All that would do is \emph{increase} the profit for the
provider because the law of large numbers would tell them
exactly how many would not go through with the abortion.
In other words, they would offer the original
bundled price because the buyers did not know that they
will change their mind
\begin{equation}
p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
\end{equation}
but the provider will have profit of
\begin{equation}
p_b - c_s - \rho c_a,
\end{equation}
which is strictly larger than the profit in either of
the other cases.
Also, they do not need to know which buyers are more
or less likely to use abortion, just that some
fraction will not use their purchased abortion.

\section{Simulation Results for 20 Periods}

\begin{table}[!htp]
\centering
\footnotesize
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_100}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
 k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
 k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
 k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
 k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
 k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
 k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
 k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
 k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\normalsize

\begin{table}[!htp]
\centering
\footnotesize
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_95}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.09 &  56.9 &  7.19 &  52.4 &  7.30 &  50.5 &  7.33 &  50.1 &  7.34 &  50.0 \\

>>>>

\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
% \usepackage[nolists,tablesfirst]{endfloat}

@@

% \date{May 2010\\ \bigskip PRELIMINARY}
\date{October 2017}

@@

\graphicspath{{../figures/}}
\DeclareGraphicsExtensions{.eps,.jpg,.pdf,.mps,.png}
\doublespacing

@@

% \section{Why Bundle Scan and Abortion?}
% The easiest way to show why a bundled service makes sense is to model 
% the provider's problem first and then show that both provider and
% buyer will be better off if a bundled service is offered.
% Take a provider with with cost, $c_a$, of providing an abortion,
% and cost, $c_s$, of providing a scan.
% These costs include expenses for equipment, labor,
% and possibly a premium for getting caught and prosecuted. 
% The provider can either charge separately for the two services,
% in which case he will charge $p_s$ for the scan and $p_a$ for
% the abortion, or he can charge $p_b$ for the bundle.
% The provider's profit if he offers the two services separately, $\pi_{sep}$,
% to $n$ buyers, who conceive girls with the probability $p(g)$, will be
% \begin{equation}
% \pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
% \end{equation}
% The first part is profit from the customers who want a scan
% and the second part is the profit from the fraction of the
% original customers who conceived a girl.
% If the provider instead offered the same $n$ buyers a bundle service
% the profit, $\pi_{bun}$, would be
% \begin{equation}
% \pi_{bun} = n p_b - n c_s - p(g) n c_a,
% \end{equation}
% since all customers pays $p_b$, all customers get a scan 
% at cost $c_s$, and the fraction $p(g)$ who conceived a girl
% would receive an abortion at cost $c_a$.
% A profit maximizing provider then picks bundled pricing if 
% $\pi_{bun} > \pi_{sep}$, or
% \begin{equation}
%  p_b > p_s + p(g) p_a.
% \end{equation}
% Assume that buyers are risk averse and that the only motivation
% for getting a prenatal sex determination test is to abort 
% female fetuses and that parents will abort the fetus if the test 
% show a female fetus (I will relax the last assumptions below).
% Furthermore, to ease exposition assume that buyers can only
% spend money on two things: consumption $c$ and prenatal sex
% determinations/abortions.
% For a buyer facing separate services the expected utility
% is then
% \begin{equation}
% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
% \end{equation}
% where the first part is the utility if the fetus is a boy
% and the buyers therefore only spend on the scan, which
% happens with probability $1-p(g)$, and the
% second part is the utility if the fetus is a female
% and they therefore also has to pay for the abortion,
% which happens with probability $p(g)$.
% For a buyer facing a bundled service the utility is simply
% \begin{equation}
% U = U(c-p_b).
% \end{equation}
% If follows from the standard assumptions about utility functions
% and the risk aversion assumption that
% \begin{equation}
% U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
% \end{equation}
% In other words risk averse buyers prefer a sure thing---where they pay 
% upfront---over the gamble that they either have a boy and pay only for the
% scanning or have a girl and pay for both the scan and the abortion.
% In fact, risk aversion implies that they are willing to pay 
% \emph{more} than the expected cost.
% In other words,
% \begin{equation}
% U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
% \end{equation}
% where $\delta$ is a positive number that depends on the
% degree of risk aversion (the more risk averse the larger
% $\delta$ is).
% The provider realizes that buyers are risk averse
% and therefore offer a bundle where the price is in 
% the range
% \begin{equation}
% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
% \end{equation}
% Hence, the optimal pricing scheme for both provider
% and buyer is bundled pricing, where you pay a flat fee
% and get the pre-natal sex determination and an abortion
% if needed.
% % Where the provider ends up in the possible range of
% % prices depends on the nature of the provider market.
% I implicitly assumed that the provider is risk-neutral.
% The same result hold, however, if the provider
% is risk-averse as long as there are enough potential clients.
% In that case, the law of large numbers will ensure that 
% the risk-neutral and risk-averse choices are the same
% for the provider---essentially there is no gamble if you see 
% enough clients, $p(g)$ of them will present with a female fetus 
% and $1-p(g)$ with a male fetus.
% In fact, it is possible for the provider to be \emph{more}
% risk averse than the buyers and still prefer the bundled 
% pricing scheme.
% Now imagine a situation where there there is some 
% uncertainty about whether a buyer will go through with
% the abortion after the prenatal sex determination.
% This can be represented by the probability $\rho$ that
% a buyer who had a prenatal sex determination test that
% showed a female fetus will go through with the abortion.
% If parents know that there is probability $1-\rho$ that they
% will not go through with the abortion their utility is
% \begin{equation}
% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
% \end{equation}
% where I have made the assumption that they
% are equally happy with a boy or a girl if they
% are in the $1-\rho$ portion of the population that
% have a prenatal sex determination which show a female
% fetus but do not go through with the abortion (obviously
% this cannot be the case because if they were there
% would be no point in having the prenatal sex determination,
% but if I can show that the bundle price arise here it
% would trivially hold if there were some lower utility
% associated with having a girl than a boy).
% Because the buyers are still risk averse they would continue
% to prefer the ``sure'' thing over the gamble
% \begin{equation}
% U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
% \end{equation}
% The provider still offers a bundle, but the price is now 
% in  the range
% \begin{equation}
% p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
% \end{equation}
% where $\delta$ still depends on the degree of risk aversion.
% If parents on the other hand initially believe that they will always
% go through with the abortion if the fetus is female but
% still have probability $1-\rho$ that they will not, they would
% be back to the original comparison of the utility.
% \begin{equation}
% U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
% \end{equation}
% All that would do is \emph{increase} the profit for the
% provider because the law of large numbers would tell them
% exactly how many would not go through with the abortion.
% In other words, they would offer the original
% bundled price because the buyers did not know that they
% will change their mind
% \begin{equation}
% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
% \end{equation}
% but the provider will have profit of
% \begin{equation}
% p_b - c_s - \rho c_a,
% \end{equation}
% which is strictly larger than the profit in either of
% the other cases.
% Also, they do not need to know which buyers are more
% or less likely to use abortion, just that some
% fraction will not use their purchased abortion.
% \clearpage
% \newpage

% \section{Simulation Results for 20 Periods}
% \begin{table}[!htp]
% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_fertility_100}
% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
% \toprule
%                & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
% \midrule
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
%  k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
%  k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
%  k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
%  k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
%  k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
%  k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
%  k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
%  k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
%  k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
%  k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
%  k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
%  k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
%  k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
%  k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
%  k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
%  k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
%  k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
%  k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
% \begin{tablenotes} \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
%  and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
% \normalsize
% \begin{table}[!htp]
% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_fertility_95}
% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
% \toprule
%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
% \midrule
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
%  k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
%  k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
%  k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
%  k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
%  k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
%  k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
